---
title: "Plot Report"
output: html_document
params:
  CountData: NA
  groupList: NA
  zeroValue: NA
  sampleDistributionBar: NA
  sampleDistributionDensity: NA
  norSampleDistributionBar: NA
  norSampleDistributionDensity: NA
  MAPlotObject: NA
  VolcanoPlotObject: NA
  screePlot: NA
  pca3d: NA
  pca2d: NA
  heatmapObject: NA
  expressionLevelBar: NA
  expressionLevelBox: NA
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, results='asis')
library(plotly)
```

# Session infomation

Generated at: `r Sys.time()`  

Size of original dataset: `r nrow(params$CountData)` rows / `r ncol(params$CountData)` column

Number of group: `r length(params$groupList)`  
Detail:  
```{r}
for(i in 1:length(params$groupList)){
  group_name <- names(params$groupList)[i]
  cat(paste0(group_name, ": ",
             paste0(params$groupList[[i]], collapse = ", "), 
             "  \n")
      )
}
```

Number of gene which expression level equal to zero in all sample: `r params$zeroValue`



## Sample Distribution  

### Sample distribution in boxplot  
```{r}
if(params$sampleDistributionBar != ""){
  params$sampleDistributionBar
} else {
  "Not available"
}
```

### Sample distribution in boxplot (normalized)  
```{r}
if(params$norSampleDistributionBar != ""){
  params$norSampleDistributionBar
} else {
  "Not available"
}
```

### Sample distribution density plot  
```{r}
if(params$sampleDistributionDensity != ""){
  params$sampleDistributionDensity
} else {
  "Not available"
}
```

### Sample distribution density plot (normalized)  
```{r}
if(params$norSampleDistributionDensity != ""){
  params$norSampleDistributionDensity
} else {
  "Not available"
}
```

## MA Plot  
```{r}
if(params$MAPlotObject != ""){
  params$MAPlotObject
} else {
  "Not available"
}
```

## Volcano Plot  
```{r}
if(params$VolcanoPlotObject != ""){
  params$VolcanoPlotObject
} else {
  "Not available"
}
```

## PCA  

### Scree plot  
```{r}
if(params$screePlot != ""){
  params$screePlot
} else {
  "Not available"
}
```

### 3D  
```{r}
if(params$pca3d != ""){
  params$pca3d
} else {
  "Not available"
}
```

### 2D  
```{r}
if(params$pca2d != ""){
  params$pca2d
} else {
  "Not available"
}
```

## Heatmap  
```{r}
if(params$heatmapObject != ""){
  params$heatmapObject
} else {
  "Not available"
}
```

## Expression Level  

### Barplot  
```{r}
if(params$expressionLevelBar != ""){
  params$expressionLevelBar
} else {
  "Not available"
}
```

### Boxplot  
```{r}
if(params$expressionLevelBox != ""){
  params$expressionLevelBox
} else {
  "Not available"
}
```
