---
title: "TCC-GUI Analysis Report"
output: html_document
params:
  CountData: NA
  groupList: NA
  result: NA
  norData: NA
  zeroValue: NA
  sampleDistributionBar: NA
  sampleDistributionDensity: NA
  norSampleDistributionBar: NA
  norSampleDistributionDensity: NA
  MAPlotObject: NA
  VolcanoPlotObject: NA
  pcTransform: NA
  pcCenter: NA
  pcScale: NA
  screePlot: NA
  pca3d: NA
  pca2d: NA
  heatmapObject: NA
  expressionLevelBar: NA
  expressionLevelBox: NA
  groupListConvert: NA
  filterLowCount: NA
  normMethod: NA
  testMethod: NA
  iteration: NA
  fdr: NA
  floorpdeg: NA
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, results='asis')
library(plotly)
library(knitr)
library(DT)
```

# Session infomation

This report is generated at: 
`r Sys.time()`  

> If "Not available" is shown in the report, it means you haven't generate the plot in TCC-GUI. Only the plot was shown in TCC-GUI at least one time, it can be output to the report.  

Size of original dataset:   
`r nrow(params$CountData)` rows  
`r ncol(params$CountData)` columns

Number of group: 
`r length(params$groupList)`  
Detail of group information (Used columns):  
```{r groupList}
for(i in 1:length(params$groupList)){
  group_name <- names(params$groupList)[i]
  cat(paste0(group_name, ": ",
             paste0(params$groupList[[i]], collapse = ", "), 
             "  \n")
      )
}
```

Number of gene which expression level equal to zero in all sample: 
`r params$zeroValue`  

# TCC Computation

This part is about TCC Computation processing.  
TCC Parameters is shown as below. 
```{r tcc parameters}
tccPara <- rbind(
  c("params$CountData", "Count data", class(params$CountData)),
  c("params$groupListConvert", "List of group infomation", class(params$groupListConvert)),
  c("params$filterLowCount", "Filter low count genes threshold", params$filterLowCount),
  c("params$normMethod", "Normalization method", params$normMethod),
  c("params$testMethod", "DEGs identify method", params$testMethod),
  c("params$iteration", "Iteration", params$iteration),
  c("params$fdr", "FDR", params$fdr),
  c("params$floorpdeg", "Elimination of potential DEGs", params$floorpdeg)
  )
colnames(tccPara) <- c("Parameters", "Explanation", "Value / class")
kable(tccPara, caption = "Paramters used in TCC computation.")
```

```{r show count data}
kable(head(params$CountData, 10), caption = "First 10 row of original dataset.")
```

List of group infomation is shown as below:  
```{r groupListConvert, results='markup'}
params$groupListConvert
```

Computation code is shown as below.  

(If you want to run this piece of code directly, loading data into your own R environment is necessary. Using `data <- data.table::fread(YOUR_FILE_PATH)` to replace `data <- params$CountData` is a highly efficiency way of reading row count text file. Next create a variable `data.cl` to save group information list.)  
```{r tcc computation, echo=TRUE, eval=FALSE}
library(TCC)
# Dataset
data <- params$CountData
# Group infomation
data.cl <- params$groupListConvert

# Create TCC Object
tcc <- new("TCC", data[data.cl != 0], data.cl[data.cl != 0])
# Filter low count genes before calculation
tcc <- filterLowCountGenes(tcc, low.count = params$filterLowCount)
# Run TCC and calculate normalized factor
tcc <- calcNormFactors(tcc, 
                       norm.method = params$normMethod,
                       test.method = params$testMethod,
                       iteration = params$iteration,
                       FDR = params$fdr,
                       floorPDEG = params$floorpdeg)

# Estimate DEGs
tcc <- estimateDE(tcc,
                  test.method = input$testMethod,
                  FDR = input$fdr)

# Get final result of TCC
result <- getResult(tcc, sort = FALSE)
norData <- tcc$getNormalizedData()
```

Here is a preview of your TCC results.  
```{r tcc result}
kable(head(params$result, 10), caption = "First 10 row of TCC result table")
kable(head(params$norData, 10), caption = "First 10 row of normalized data")
```

## Sample Distribution  

### Sample distribution in boxplot  
```{r}
if(params$sampleDistributionBar != ""){
  params$sampleDistributionBar
} else {
  "Not available"
}
```

### Sample distribution in boxplot (normalized)  
```{r}
if(params$norSampleDistributionBar != ""){
  params$norSampleDistributionBar
} else {
  "Not available"
}
```

### Sample distribution density plot  
```{r}
if(params$sampleDistributionDensity != ""){
  params$sampleDistributionDensity
} else {
  "Not available"
}
```

### Sample distribution density plot (normalized)  
```{r}
if(params$norSampleDistributionDensity != ""){
  params$norSampleDistributionDensity
} else {
  "Not available"
}
```

## MA Plot  
```{r}
if(params$MAPlotObject != ""){
  params$MAPlotObject
} else {
  "Not available"
}
```

## Volcano Plot  
```{r}
if(params$VolcanoPlotObject != ""){
  params$VolcanoPlotObject
} else {
  "Not available"
}
```

## Principal Components Analysis  

PCA parameters is shown as below:

```{r pca para}
pcaPara <- rbind(
  c("data", "Data source", "data.frame"),
  c("input$pcFDR", "FDR Cut-off", params$pcFDR),
  c("input$pcTransform", "Log(x+1) transform", params$pcTransform),
  c("input$pcCenter", "Center", params$pcCenter),
  c("input$pcScale", "Scale", params$pcScale)
  )
  colnames(pcaPara) <-
  c("Parameter", "Explanation", "Value / Class")
  kable(pcaPara, caption = "Paramters used in PCA.")
```

Computation code is shown as below.  
Reload `result` and `norData` from the previous TCC computation part.

```{r pca computation, echo=TRUE, eval=FALSE}
# Get final result of TCC
# result <- getResult(tcc, sort = FALSE)
# norData <- tcc$getNormalizedData()
```

### Scree plot  
```{r}
if(params$screePlot != ""){
  params$screePlot
} else {
  "Not available"
}
```

### 3D  
```{r}
if(params$pca3d != ""){
  params$pca3d
} else {
  "Not available"
}
```

### 2D  
```{r}
if(params$pca2d != ""){
  params$pca2d
} else {
  "Not available"
}
```

## Heatmap  
```{r}
if(params$heatmapObject != ""){
  params$heatmapObject
} else {
  "Not available"
}
```

## Expression Level  

### Barplot  
```{r}
if(params$expressionLevelBar != ""){
  params$expressionLevelBar
} else {
  "Not available"
}
```

### Boxplot  
```{r}
if(params$expressionLevelBox != ""){
  params$expressionLevelBox
} else {
  "Not available"
}
```
